%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Kendra K. Noneman} % Your name
\address{knoneman@andrew.cmu.edu \hspace{2mm} \\ \hspace{2mm} kendranoneman.com} % Your phone number and email
\address{github.com/kendranoneman}
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf{Carnegie Mellon University}} \hfill {2020 -} \\ 
Ph.D. Program in Neural Computation, \textit{3.75 GPA} \\
Center for the Neural Basis of Cognition \\
Advisor: J. Patrick Mayo, Ph.D. \smallskip 

{\bf Boise State University} \hfill {2016 - 2020} \\ 
B.S. in Materials Science and Engineering, \textit{magna cum laude} \\
Minor in Applied Mathematics \smallskip

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Mayo Lab}{2021 -}{Graduate Research Assistant}{}
\item University of Pittsburgh, Department of Ophthalmology
%\item Studying the influence of eye movements on populations of visual neurons in cerebral cortex
%\item Use electrophysiology and computational methods to uncover the fundamental principles of natural primate vision
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Smith Lab \& Yu Lab}{Fall 2020}{Graduate Rotation Student}{}
\item Carnegie Mellon University, Neuroscience Institute
%\item Studying the influence of eye movements on populations of visual neurons in cerebral cortex
%\item Use electrophysiology and computational methods to uncover the fundamental principles of natural primate vision
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Computational Materials Engineering Lab}{2015 - 2020}{Undergraduate Research Assistant}{}
\item Boise State University, ID
%\item Researched the self-assembly of small-molecule semiconductors and their application to organic photovoltaics on the largest academic supercomputer in US
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{CoAx Lab}{Summer 2019}{Research Fellow, Program in Neural Computation}{}
\item Carnegie Mellon University, PA
%\item Investigated how circuit-level properties and dopaminergic plasticity of cortico-basal-ganglia-thalamic (CBGT) networks influences decision-making
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Applied Materials}{Summer 2018}{Process Engineering and Data Analysis Intern}{}
\item Micron Customer Division, ID
%\item Created software framework for big data processing using Excel, SQL, and Tableau
%\item Matched performance metrics for chemical vapor deposition and reactive ion etch hardware
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{NASA Ames Research Center}{Summer 2017}{Computational Quantum Astrochemistry Intern}{}
\item Space Sciences and Astrophysics Branch, CA
%\item Utilized state-of-the-art quantum chemistry methods (Density-Functional theory and Coupled Cluster theory) to analyze spectra data for molecules in space
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{National Center for Supercomputing Applications}{2016 - 2017}{Blue Waters High-Performance Computing Intern}{}
\item University of Illinois in Urbana-Champaign, IL
%\item Invited to an intensive two-week Petascale Institute at the University of Illinois in Urbana-Champaign
%\item Received 16,000 GPU-hour allocation on Blue Waters Supercomputer for my work in the Computational Materials Engineering Lab
\end{rSubsection}

\end{rSection}

\newpage
%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\begin{rSection}{Publications}
\begin{rSubsection4}{Peer-Reviewed Journal Articles}{}{}{}
\item "Energy Landscape, and Structural and Spectroscopic Characterization of Diazirine and Its Cyclic Isomers." PP Bera, \textbf{KK Noneman}, TJ Lee. \textit{Journal of Physical Chemistry A}, Submitted (2022).
\item “Molecular simulations for understanding the stabilization of fullerenes in water.” \textbf{K Noneman}, C Muhich, K Ausman, M Henry, E Jankowski. \textit{Journal of Computational Science Education}, https://doi.org/10.22369/issn.2153-4136/12/1/6 (2021).
\item “The credit assignment problem in cortico‐basal ganglia‐thalamic networks: A review, a problem and a possible solution.” JE Rubin, C Vich, M Clapp, \textbf{K Noneman}, T Verstynen. \textit{European Journal of Neuroscience}, https://doi.org/10.1111/ejn.14745 (2020).
\item “Perspective on Coarse-Graining, Cognitive Load, and Materials Simulation.” E Jankowski, N Ellyson, JW Fothergill, MM Henry, MH Leibowitz, ED Miller, S Chesser, JD Guevara, CD Jones, M Klopfenstein, \textbf{KK Noneman}, R Singleton, RA Uriarte-Mendoza, S Thomas, CE Estridge, ML Jones. \textit{Computational Materials Science}, https://doi.org/10.1016/j.commatsci.2019.109129 (2020).
\end{rSubsection4}
    
\begin{rSubsection4}{Conference Presentations}{}{}{}
\item "Neuronal populations trajectories during smooth pursuit and motion perturbations in area MT", Society for Neuroscience Annual Meeting, Poster, Chicago, IL (2021). 
\item “Simulating the Effects of Dopaminergic Plasticity on Cortico-Basal-Ganglia-Thalamic (CBGT) Networks”, Center for Neural Basis of Cognition (CNBC), Poster, Pittsburgh, PA (2019).
\item “Characterization of Diazirine and its Isomers”, NASA Ames Research Center (Space Science and Astrobiology), Poster, Mountain View, CA (2017).
\item “Molecular Simulations of Fullerene Stabilization in Water by Fullerene-Oxides”, American Institute of Chemical Engineering (AIChE) Annual Meeting, Poster, Minneapolis, MN (2017).
\end{rSubsection4}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Service and Leadership}
{\bf President of Executive Board} \hfill {2022 -} \\ 
Neuroscience Institute Student Organization \\
Carnegie Mellon University, PA \smallskip 

{\bf Co-chair, Colliquium Committee} \hfill {2021 -} \\ 
Center for the Neural Basis of Cognition (CNBC) \\
Carnegie Mellon University, PA \smallskip

{\bf Department Representative} \hfill {2021 -} \\ 
Graduate Student Assembly (GSA) \\
Carnegie Mellon University, PA \smallskip

{\bf Chapter President} \hfill {2018 - 2020} \\ 
Tau Beta Pi Engineering Honor Society \\
Boise State University - ID Gamma Chapter \smallskip

{\bf Representative of Student-Athlete Advisory Committee (SAAC)} \hfill {2018 - 2020} \\ 
NCAA Division I Track and Field \\
Boise State University, ID \smallskip

{\bf Awards Committee Chair and Host} \hfill {2019} \\ 
Tau Beta Pi National Convention \\
Ohio State University, OH \smallskip

\end{rSection}

\newpage
%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Recognition}
\begin{rSubsection2}{Awards \& Honors}{}{}{}
\item Center for Visual Science Travel Fellowship (2022)
\item NCAA Division III National Athlete of the Week (2022)
\item University Athletic Association Athlete of the Week (2022)
\item SfN Trainee Professional Development Award (2021)
\item Mountain West Scholar Athlete of the Year (2020)
\item Boise State Athletics Academic Excellence Award (2020) 
\item Boise State Top Ten Scholar (2020)
\item Boise State Graduating Student Leader Award (2020)
\item Tau Beta Pi Fellowship Award (2020)
\item NCAA Division 1 All-Academic Athlete (2019) 
\item AIST Northwest Member Chapter Scholarship (2019)
\item Tau Beta Pi Laureate Award (2019)
\item Tau Beta Pi Scholarship (2019)
\item University Space Research Association Honorable Mention (2019)
\item Mountain West All-Academic Athlete (2017-2020)
\item Boise State High Honors Dean’s List (2016-2020)
\item American Council of Engineering Companies Scholarship (2018)
\item University Space Research Association Honorable Mention (2018)
\item Marines’ Memorial Association Scholarship (2018)
\item Idaho NASA Space Grant Consortium Scholarship (2017)
\item National Science Foundation Scholarship (2017)
\item Engineering Department: Going-the-Extra-Mile Award (2017)
\item Boise State Presidential Scholarship (2016)
\item Idaho Governor’s Cup Scholarship (2016)
\item Society of Women Engineers Northwest ID Scholarship (2016)
\end{rSubsection2}
\begin{rSubsection3}{Feature Articles}{}{}{}
\item "Boise State's Noneman honored as Mountain West Female Scholar-Athlete of the Year." \textit{Mountain West Athlete Awards}, themw.com/news/2020/7/30/athlete-awards-boise-states-noneman-honored-as-mountain-west-female-scholar-athlete-of-the-year.aspx (2020).
\item "Boise State Alumni Association honors Top 10 Scholars at virtual May 7 event." \textit{Boise State News}, www.boisestate.edu/news/2020/04/23/boise-state-alumni-association-honors-top-10-scholars-at-virtual-may-7-event/ (2020).
\item "Materials science and engineering athlete recognized for excellence." \textit{Boise State News}, www.boisestate.edu/news/2019/10/02/mechanical-science-and-engineering-athlete-kendra-noneman-recognized-for-excellence/ (2019).
\item "Tau Beta Pi Announces 2019 Laureates." \textit{Tau Beta Pi Engineering Honor Society Newsletter}, www.tbp.org/memb/LaureatePDFs/2019.pdf (2019).
\item "The Journey from High School Intern to Undergraduate Researcher." \textit{Boise State News}, www.boisestate.edu/news/2016/06/29/yearlong-journey-high-school-intern-undergraduate-researcher/ (2016).
\item "Eagle teen jump-starts engineering career." \textit{Idaho Education News}, www.idahoednews.org/features/eagle-teen-jump-starts-engineering-career/ (2016).
\end{rSubsection3}
\end{rSection}
\newpage

%----------------------------------------------------------------------------------------
%	ACTIVITIES SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Other Activities}
\begin{rSubsection2}{Professional}{}{}{}
\item Student, Neuromatch Academy Computational Neuroscience course (2021).
\item Volunteer and Mentor, CMU Graduate Student Interviews (2021).
\item Representative and Chair, Tau Beta Pi National Convention (2019). 
\item Attendee, Boise State Women in Leadership Luncheon (2019).
\item Attendee, Idaho National Laboratory Luncheon (2019).
\item Guest Speaker, BSU Engineering Living-Learning Community Orientation (2018).
\item Attendee, BSU Athletics Varsity-B Mixer (2018).
\item Team Lead, BSU Virtually-Integrated Projects (2018).
\item Assistant, Software Carpentry Workshop (2018).
\item Attendee, BSU Athletics Varsity-B Mixer (2017).
\item Guest Speaker, Idaho Science and Aerospace Scholars (2017).
\end{rSubsection2}
\begin{rSubsection2}{Community Outreach}{}{}{}
\item Volunteer, BSU BroncoBold Mental Health Initiative (2019). 
\item Volunteer, Tau Beta Pi "Rake Up Boise" Event (2019).
\item Volunteer, Bronco Athletics Association Appreciation Day (2019).
\item Mentor, Ada County Juvenile Detention Center (2019).
\item Volunteer, Pittsburgh Pride Parade (2019).
\item Coordinator, Boise State "STEM on the Blue Event" (2019).
\item Volunteer, BSU Athletics Endowment Event (2018).
\item Volunteer, San Francisco Pride Parade Volunteer (2017).
\item Volunteer, Make a WIsh Foundation: "Serving up Wishes Event" (2016). 
\end{rSubsection2}
\begin{rSubsection2}{Athletics}{}{}{}
\item Hammer Thrower (School Record Holder), Carnegie Mellon Track and Field (2021 -).
\item Hammer Thrower \& Team Manager, Boise State Track and Field (2016 - 2020).
\end{rSubsection2}
\end{rSection}


%----------------------------------------------------------------------------------------
%	MENTORSHIP
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}
%Section content\ldots
%\end{rSection}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	RESEARCH SUPPORT
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}
%Section content\ldots
%\end{rSection}

%----------------------------------------------------------------------------------------


\end{document}
