%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
    citecolor=black,
    filecolor=black
}

\name{Kendra K. Noneman} % Your name 
\vspace*{-0.5mm}
\address{knoneman@andrew.cmu.edu \hspace{1.5mm} \\ \hspace{1.5mm} 208-914-3301} 
% Your phone number and email 
%\address{\underline{github.com/kendranoneman}}
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{center}
\vspace*{1mm} 
{\huge \href{https://github.com/kendranoneman}{\faGithub}}\hspace{3mm}
{\huge \href{https://www.linkedin.com/in/kendranoneman/}{\faLinkedinSquare}} \hspace{3mm}
{\huge \href{https://twitter.com/kendranoneman}{\faTwitter}} \hspace{3mm}
{\huge \href{https://www.mayolab.net}{\faFlask}
}\\
\end{center}

\begin{rSection}{Education}
{\bf Carnegie Mellon University} \hfill {2020 -} \\ 
Ph.D. Program in Neural Computation \\
Neuroscience Institute, Center for the Neural Basis of Cognition \\
(Advisor: J. Patrick Mayo) \smallskip 

{\bf Boise State University} \hfill {2016 - 2020} \\ 
B.S. in Materials Science and Engineering, \textit{magna cum laude} \\
Minor in Applied Mathematics, Emphasis in Scientific Computing \\
{\bf \textit{Top Ten Scholar, Mountain West Scholar Athlete of the Year}} \\ 
(Advisor: Eric Jankowski) \smallskip

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{Visual-Motor Neuroscience Laboratory, University of Pittsburgh}{Feb 2021 -}{Graduate Research Assistant}{}
\item (Advisor: J. Patrick Mayo)
\begin{itemize}
    \item Conducting research on the cortical representations underlying eye movements and visual perception, using electrophysiology, eye tracking, and machine learning tools. 
    \item Helped design and construct the lab's recording and data collection setup.
    \item Developed code for data pipelines, high-performance computing, and analysis, and established our lab's presence on GitHub.
    \item Collaborated with clinical research groups and other labs to extract eye traces from videos of patients and assisted them in using eye-tracking glasses.
    \item Manuscript as first author in progress and posters presented at 4 conferences. 
\end{itemize}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Neuroscience Institute, Carnegie Mellon University}{Aug 2020 - Jan 2021}{Graduate Rotation Student}{}
\item (Advisors: Matthew Smith, Byron Yu)
\begin{itemize}
    \item Conducted research on the voluntary control of internal states via brain-computer interfaces, using invasive recordings and dimensionality reduction methods.
\end{itemize}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Computational Materials Lab, Boise State University}{Aug 2015 - May 2020}{Undergraduate Research Assistant}{}
\item (Advisor: Eric Jankowski)
\begin{itemize}
    \item Conducted research on the self-assembly of small-molecule semiconductors and their application to organic photovoltaics on the largest academic supercomputer in US.
    \item Manuscript as first author published and poster presented at major conference. 
\end{itemize}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{CoAx Lab, Carnegie Mellon University}{Jun 2019 - Aug 2019}{Research Fellow, Program in Neural Computation}{}
\item (Advisors: Timothy Verstynen, Jon Rubin)
\begin{itemize}
    \item Investigated how circuit-level properties and dopaminergic plasticity of cortico-basal-ganglia-thalamic (CBGT) networks influences decision-making.
    \item Manuscript published and poster presented at internal conference. 
\end{itemize}
\end{rSubsection}

%------------------------------------------------
\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{rSection}{Industry Experience}

\begin{rSubsection}{Applied Materials, Micron Semiconductor Division}{May 2018 - Aug 2018}{Process Engineering and Data Analytics Intern}{}
\item (Mentors: Kyle Hancock, Ian )
\begin{itemize}
    \item Created software (SQL,Tableu) framework for big data processing pipeline, matching performance merics for chemical vapor deposition and reactive ion etch hardware.
    \item Assisted with onboarding and debugging new chambers at multiple fabrication facilities.
\end{itemize}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{NASA Ames Research Center, Astrophysics Branch}{Jun 2017 - Aug 2017}{Computational Quantum Astrochemistry Intern}{}
\item (Mentors: Partha Bera, Tim ) 
\begin{itemize}
    \item Utilized state-of-the-art quantum chemistry methods (Density-Functional theory and Coupled Cluster theory) and HPC clusters to analyze spectra data for astrophysical molecules.
    \item Manuscript as 2nd author published and poster presented at NASA-wide conference. 
\end{itemize}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{National Center for Supercomputing Applications, Blue Waters}{May 2016 - May 2017}{High-Performance Computing Intern}{}
\item University of Illinois in Urbana-Champaign, IL
\begin{itemize}
    \item Invited to an intensive two-week Petascale Institute at the University of Illinois in Urbana-Champaign, where specific emphasis was placed on GPU parallelization
    \item Received 16,000 GPU-hour allocation on Blue Waters Supercomputer for my work at Boise State, resulting in a first author publication
\end{itemize}
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\begin{rSection}{Publications}
\begin{rSubsection4}{Peer-Reviewed Journal Articles}{}{}{}
\item “Gaze decoding with sensory and motor cortical activity." \textbf{KK Noneman}, JP Mayo. \textit{Proceedings of the 2024 Symposium on Eye Tracking Research and Applications},\\ \href{https://doi.org/10.1145/3649902.3655655}{https://doi.org/10.1145/3649902.3655655} (2024).
\item “Energy Landscape, and Structural and Spectroscopic Characterization of Diazirine and Its Cyclic Isomers." PP Bera, \textbf{KK Noneman}, TJ Lee. \textit{Journal of Physical Chemistry A}, \\ \href{https://doi.org/10.1021/acs.jpca.2c01444}{https://doi.org/10.1021/acs.jpca.2c01444} (2022).
\item “Molecular simulations for understanding the stabilization of fullerenes in water.” \textbf{K Noneman}, C Muhich, K Ausman, M Henry, E Jankowski. \textit{Journal of Computational Science Education}, \href{https://doi.org/10.22369/issn.2153-4136/12/1/6}{https://doi.org/10.22369/issn.2153-4136/12/1/6} (2021).
\item “The credit assignment problem in cortico‐basal ganglia‐thalamic networks: A review, a problem and a possible solution.” JE Rubin, C Vich, M Clapp, \textbf{K Noneman}, T Verstynen. \textit{European Journal of Neuroscience}, \href{https://doi.org/10.1111/ejn.14745}{https://doi.org/10.1111/ejn.14745} (2020).
\item “Perspective on Coarse-Graining, Cognitive Load, and Materials Simulation.” E Jankowski, N Ellyson, JW Fothergill, MM Henry, \textbf{KK Noneman}, et al. \textit{Computational Materials Science}, \href{https://doi.org/10.1016/j.commatsci.2019.109129}{https://doi.org/10.1016/j.commatsci.2019.109129} (2020).
\end{rSubsection4}
    
\begin{rSubsection4}{Conference Presentations}{}{}{}
\item “Gaze decoding with sensory and motor cortical activity", ACM Symposium on Eye Tracking Research and Applications, Poster, Glasgow, UK (2024).
\item “Decoding Smooth Pursuit Eye Movements from Area MT and FEF Neuronal Responses", Gordon Research Conference on Eye Movements, Poster, Mount Holyoke, MA (2023).
\item “Modulation of frontal eye field neuronal activity during saccades and smooth pursuit", Center for Visual Science Syposium on Active Vision, Poster, Rochester, NY (2022).
\item “Neuronal populations trajectories during smooth pursuit and motion perturbations in area MT", Society for Neuroscience Annual Meeting, Poster, Chicago, IL (2021). 
\item “Simulating the Effects of Dopaminergic Plasticity on Cortico-Basal-Ganglia-Thalamic (CBGT) Networks”, Center for Neural Basis of Cognition (CNBC), Poster, Pittsburgh, PA (2019).
\item “Characterization of Diazirine and its Isomers”, NASA Ames Research Center (Space Science and Astrobiology), Poster, Mountain View, CA (2017).
\item “Molecular Simulations of Fullerene Stabilization in Water by Fullerene-Oxides”, American Institute of Chemical Engineering (AIChE) Annual Meeting, Poster, Minneapolis, MN (2017).
\end{rSubsection4}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Service and Leadership}
{\bf President of Executive Board} \hfill {2022 - 2023} \\ 
Neuroscience Institute Student Organization \\
Carnegie Mellon University, PA \smallskip 

{\bf Co-chair, Colliquium Committee} \hfill {2021 - 2023} \\ 
Center for the Neural Basis of Cognition (CNBC) \\
Carnegie Mellon University, PA \smallskip

{\bf Department Representative} \hfill {2021 - 2022} \\ 
Graduate Student Assembly (GSA) \\
Carnegie Mellon University, PA \smallskip

{\bf Chapter President} \hfill {2018 - 2020} \\ 
Tau Beta Pi Engineering Honor Society \\
Boise State University - ID Gamma Chapter \smallskip

{\bf Representative of Student-Athlete Advisory Committee (SAAC)} \hfill {2018 - 2020} \\ 
NCAA Division I Track and Field \\
Boise State University, ID \smallskip

{\bf Awards Committee Chair and Host} \hfill {2019} \\ 
Tau Beta Pi National Convention \\
Ohio State University, OH \smallskip

\end{rSection}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Recognition}
\begin{rSubsection2}{Awards \& Honors}{}{}{}
\item Neuroscience Institute Student Community Service Award (2024)
\item Center for Visual Science Travel Fellowship (2022)
\item NCAA Division III National Athlete of the Week (2022)
\item University Athletic Association Athlete of the Week (2022)
\item SfN Trainee Professional Development Award (2021)
\item Mountain West Scholar Athlete of the Year (2020)
\item Boise State Athletics Academic Excellence Award (2020) 
\item Boise State Top Ten Scholar (2020)
\item Boise State Graduating Student Leader Award (2020)
\item Tau Beta Pi Fellowship Award (2020)
\item AIST Northwest Member Chapter Scholarship (2019)
\item Tau Beta Pi Laureate Award (2019)
\item Tau Beta Pi Scholarship (2019)
\item University Space Research Association Honorable Mention (2019)
\item Mountain West All-Academic Athlete (2017-2020)
\item Boise State High Honors Dean’s List (2016-2020)
\item American Council of Engineering Companies Scholarship (2018)
\item University Space Research Association Honorable Mention (2018)
\item Marines’ Memorial Association Scholarship (2018)
\item Idaho NASA Space Grant Consortium Scholarship (2017)
\item Engineering Department: Going-the-Extra-Mile Award (2017)
\item Boise State Presidential Scholarship (2016)
\item Idaho Governor’s Cup Scholarship (2016)
\item Society of Women Engineers Northwest ID Scholarship (2016)
\end{rSubsection2}

\begin{rSubsection3}{Feature Articles}{}{}{}
\item \href{https://www.cmu.edu/dietrich/news/news-stories/2022/may/hammer-kendra-noneman.html}{“Division III top-ranked thrower and neuroscientist, Kendra Noneman, heads to nationals."} \textit{Carnegie Mellon University Features} (2022).
\item \href{https://broncosports.com/news/2020/7/30/general-noneman-named-mw-scholar-athlete-of-the-year}{“Boise State's Noneman honored as Mountain West Female Scholar-Athlete of the Year."} \textit{Mountain West Athlete Awards} (2020).
\item \href{www.boisestate.edu/news/2020/04/23/boise-state-alumni-association-honors-top-10-scholars-at-virtual-may-7-event/}{“Boise State Alumni Association honors Top 10 Scholars at virtual May 7 event."} \textit{Boise State News} (2020).
\item \href{www.boisestate.edu/news/2019/10/02/mechanical-science-and-engineering-athlete-kendra-noneman-recognized-for-excellence/}{“Materials science and engineering athlete recognized for excellence."} \textit{Boise State News} (2019).
\item \href{www.tbp.org/memb/LaureatePDFs/2019.pdf}{“Tau Beta Pi Announces 2019 Laureates."} \textit{Tau Beta Pi Engineering Honor Society Newsletter} (2019).
\item \href{www.boisestate.edu/news/2016/06/29/yearlong-journey-high-school-intern-undergraduate-researcher/}{“The Journey from High School Intern to Undergraduate Researcher."} \textit{Boise State News} (2016).
\item \href{www.idahoednews.org/features/eagle-teen-jump-starts-engineering-career/}{“Eagle teen jump-starts engineering career."} \textit{Idaho Education News} (2016).
\end{rSubsection3}
\end{rSection}

%----------------------------------------------------------------------------------------
%	ACTIVITIES SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Other Activities}
\begin{rSubsection2}{Teaching}{}{}{}
\item Teaching Assistant, Foundations of the Neural Basis of Cognition taught by Patrick Mayo (2024).
\item Brain-Bots Course Co-Instructor, Leonard Gelfand Center for Service Learning and Outreach (2023).
\item Teaching Assistant, Neural Engineering Laboratory taught by Douglas Weber and Matthew Smith (2023).
\end{rSubsection2}
\begin{rSubsection2}{Professional}{}{}{}
\item Student Host and visit organizer, CNBC Colloquium Speaker Series: Konrad Kording (2024).
\item Student Host and visit organizer, CNBC Colloquium Speaker Series: Eli Merriam (2024).
\item Student Representative, Faculty Search Committee (2023).
\item Student Host and visit organizer, CNBC Colloquium Speaker Series: David Sussillo (2022).
\item Student, Neuromatch Academy Computational Neuroscience course (2021).
\item Volunteer and Mentor, CMU Graduate Student Interviews (2021).
\item Representative and Chair, Tau Beta Pi National Convention (2019). 
\item Attendee, Boise State Women in Leadership Luncheon (2019).
\item Attendee, Idaho National Laboratory Luncheon (2019).
\item Guest Speaker, BSU Engineering Living-Learning Community Orientation (2018).
\item Attendee, BSU Athletics Varsity-B Mixer (2018).
\item Team Lead, BSU Virtually-Integrated Projects (2018).
\item Assistant, Software Carpentry Workshop (2018).
\item Attendee, BSU Athletics Varsity-B Mixer (2017).
\item Guest Speaker, Idaho Science and Aerospace Scholars (2017).
\end{rSubsection2}

\begin{rSubsection2}{Community Outreach}{}{}{}
\item Career Panelist \& Volunteer, Psychology and Neuroscience SciTech Days (2024).
\item Volunteer Instructor, Rehabilitation and Neural Engineering Laboratory Adult Coding Class (2023).
\item Career Panelist \& Volunteer, Health and Fitness SciTech Days (2023).
\item Category Judge, Pittsburgh Science Fair (2022).
\item Volunteer, BSU BroncoBold Mental Health Initiative (2019). 
\item Volunteer, Tau Beta Pi "Rake Up Boise" Event (2019).
\item Volunteer, Bronco Athletics Association Appreciation Day (2019).
\item Mentor, Ada County Juvenile Detention Center (2019).
\item Volunteer, Pittsburgh Pride Parade (2019).
\item Coordinator, Boise State "STEM on the Blue Event" (2019).
\item Volunteer, BSU Athletics Endowment Event (2018).
\item Volunteer, San Francisco Pride Parade Volunteer (2017).
\item Volunteer, Make a WIsh Foundation: "Serving up Wishes Event" (2016). 
\end{rSubsection2}
\begin{rSubsection2}{Athletics}{}{}{}
\item Assistant Coach, Carnegie Mellon Track and Field (2022 - 2023). 
\item Hammer Thrower (School Record, National Runner-Up), Carnegie Mellon (2021 - 2022).
\item Hammer Thrower \& Team Manager, Boise State Track and Field (2016 - 2020).
\end{rSubsection2}
\end{rSection}


%----------------------------------------------------------------------------------------
%	MENTORSHIP
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}
%Section content\ldots
%\end{rSection}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	RESEARCH SUPPORT
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}
%Section content\ldots
%\end{rSection}

%----------------------------------------------------------------------------------------


\end{document}
